---
title: "Paper Descriptives Twitter Deutschland"
author: "Lennart Klein, Conrad Borchers"
date: "`r format(Sys.time(), '%d. %B, %Y')`"
output:
  html_document:
    toc: true
    # toc_float: true
    highlight: "tango"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
```

## Load Data
```{r load data}
dat <- readRDS("/Volumes/HiWi_Data/DATA/matched_hashtags_data.rds")
```

## Setup Print Function
```{r print function}
summary_kable <- function(x, caption = NULL, col.names = NA) {
  kable(x,
    caption = caption,
    align = "c",
    digits = 2,
    col.names = col.names,
    label = NULL,
    format.args = list(scientific = FALSE) # prevent scientific notation of numerals
  ) %>%
    kable_styling(
      bootstrap_options = c("striped", "condensed", "responsive"),
      full_width = TRUE,
      fixed_thead = TRUE # freeze header to top
    )
}
```


## Dataset Summary
```{r dataset summary}
dat %>%
  summarise(
    N_tweets = n(),
    N_unique_tweets = n() - sum(is_retweet),
    N_users = length(unique(user_id)),
    tweets_per_user = n() / length(unique(user_id)),
    first_tweet = as.Date(min(created_at)),
    last_tweet = as.Date(max(created_at)),
    first_dl = as.Date(min(dl_at)),
    last_dl = as.Date(max(dl_at)),
    rt_M = mean(retweet_count, na.rm = TRUE),
    rt_SD = sd(retweet_count, na.rm = TRUE),
  ) %>%
  summary_kable(
    "Global Dataset Summary",
    c(
      "N_tweets",
      "N Original Tweets",
      "N_users",
      "Tweets_per_User",
      "first_tweet",
      "last_tweet",
      "first_dl",
      "last_dl",
      "M", "SD"
    )
  ) %>%
  add_header_above(c(" " = 4, "Timeframe" = 2, "Download Times" = 2, "Retweets" = 2))
```

# New Descriptives

## Nach Fächern

### Report Overlap
```{r}
# Ohne Retweets und nur auf Hashtags basierend
dat %>%
  filter(!is_retweet) %>%
  count(fach_checksum) %>%
  summary_kable(
    "Fächer Hashtag Communities - Overlap Report",
    c("In # Fächern", "N Original Tweets")
  )
```
### Fach Coding
- 21 Fächer (Stand: Nov 2020)

Fach         | Variable
-------------|---------------
Biologie     | has_biologie
Chemie       | has_chemie
Deutsch      | has_deutsch
Englisch     | has_englisch
Erdkunde     | has_erdkunde
Ethik        | has_ethik
Franzoesisch | has_franzoesisch
Geschichte   | has_geschichte
Informatik   | has_informatik
Kunst        | has_kunst
Mathe        | has_mathe
Musik        | has_musik
Paedagokik   | has_paedagogik
Philosophie  | has_philosophie
Physik       | has_physik
Politik      | has_politik
Psychologie  | has_psychologie
Religion     | has_religion
Spanisch     | has_spanisch
Sport        | has_sport
Wirtschaft   | has_wirtschaft  



```{r subject helper funtions}
# Tweet Level Subject counter
summarise_subjects.tweets <- function(data, category = "") {
  return(data %>%
    summarise(
      category = category,
      N = n(),
      Biologie = sum(has_biologie),
      Chemie = sum(has_chemie),
      Deutsch = sum(has_deutsch),
      Englisch = sum(has_englisch),
      Erdkunde = sum(has_erdkunde),
      Ethik = sum(has_ethik),
      Franzoesisch = sum(has_franzoesisch),
      Geschichte = sum(has_geschichte),
      Informatik = sum(has_informatik),
      Kunst = sum(has_kunst),
      Mathe = sum(has_mathe),
      Musik = sum(has_musik),
      Paedagokik = sum(has_paedagogik),
      Philosophie = sum(has_philosophie),
      Physik = sum(has_physik),
      Politik = sum(has_politik),
      Psychologie = sum(has_psychologie),
      Religion = sum(has_religion),
      Spanisch = sum(has_spanisch),
      Sport = sum(has_sport),
      Wirtschaft = sum(has_wirtschaft)
    ))
}

# User-level aggregation summary function, counter
summarise_subjects.users <- function(data, category = "") {
  return(data %>%
    summarise(
      category = category,
      N = length(unique(user_id[fach_checksum > 0])), # TODO: check validity
      Biologie = length(unique(user_id[has_biologie == 1])),
      Chemie = length(unique(user_id[has_chemie == 1])),
      Deutsch = length(unique(user_id[has_deutsch == 1])),
      Englisch = length(unique(user_id[has_englisch == 1])),
      Erdkunde = length(unique(user_id[has_erdkunde == 1])),
      Ethik = length(unique(user_id[has_ethik == 1])),
      Franzoesisch = length(unique(user_id[has_franzoesisch == 1])),
      Geschichte = length(unique(user_id[has_geschichte == 1])),
      Informatik = length(unique(user_id[has_informatik == 1])),
      Kunst = length(unique(user_id[has_kunst == 1])),
      Mathe = length(unique(user_id[has_mathe == 1])),
      Musik = length(unique(user_id[has_musik == 1])),
      Paedagokik = length(unique(user_id[has_paedagogik == 1])),
      Philosophie = length(unique(user_id[has_philosophie == 1])),
      Physik = length(unique(user_id[has_physik == 1])),
      Politik = length(unique(user_id[has_politik == 1])),
      Psychologie = length(unique(user_id[has_psychologie == 1])),
      Religion = length(unique(user_id[has_religion == 1])),
      Spanisch = length(unique(user_id[has_spanisch == 1])),
      Sport = length(unique(user_id[has_sport == 1])),
      Wirtschaft = length(unique(user_id[has_wirtschaft == 1]))
    ))
}
```

```{r}
# Tweet Level Tweet Level Stats
# FIXME: kein summarise mehr nötig oder?
subject_stats.tweets <- function(d, category = "", FUN, var) {
  return(d %>%
    summarise(
      category = category,
      N = NA,
      Biologie = FUN(pull(d[d$has_biologie == 1, var])),
      Chemie = FUN(pull(d[d$has_chemie == 1, var])),
      Deutsch = FUN(pull(d[d$has_deutsch == 1, var])),
      Englisch = FUN(pull(d[d$has_englisch == 1, var])),
      Erdkunde = FUN(pull(d[d$has_erdkunde == 1, var])),
      Ethik = FUN(pull(d[d$has_ethik == 1, var])),
      Franzoesisch = FUN(pull(d[d$has_franzoesisch == 1, var])),
      Geschichte = FUN(pull(d[d$has_geschichte == 1, var])),
      Informatik = FUN(pull(d[d$has_informatik == 1, var])),
      Kunst = FUN(pull(d[d$has_kunst == 1, var])),
      Mathe = FUN(pull(d[d$has_mathe == 1, var])),
      Musik = FUN(pull(d[d$has_musik == 1, var])),
      Paedagokik = FUN(pull(d[d$has_paedagogik == 1, var])),
      Philosophie = FUN(pull(d[d$has_philosophie == 1, var])),
      Physik = FUN(pull(d[d$has_physik == 1, var])),
      Politik = FUN(pull(d[d$has_politik == 1, var])),
      Psychologie = FUN(pull(d[d$has_psychologie == 1, var])),
      Religion = FUN(pull(d[d$has_religion == 1, var])),
      Spanisch = FUN(pull(d[d$has_spanisch == 1, var])),
      Sport = FUN(pull(d[d$has_sport == 1, var])),
      Wirtschaft = FUN(pull(d[d$has_wirtschaft == 1, var]))
    ))
}
```

```{r}
# Select only relevant tweets (with bundesland hashtag)
d <- dat %>% filter(fach_checksum > 0) # save some time in sum calcs

descr <-
  rbind(
    d %>%
      summarise_subjects.users("Users"),
    # Tweets
    d %>%
      filter(!is_retweet) %>% # only original tweets
      summarise_subjects.tweets("Original Tweets"),
    # Retweets
    d %>%
      filter(is_retweet) %>%
      summarise_subjects.tweets("Retweets"),
    # Quotes
    d %>%
      filter(is_quote) %>%
      summarise_subjects.tweets("Quotes"),
    # Media
    d %>%
      filter(!is.na(media_url)) %>%
      summarise_subjects.tweets("Media"),

    subject_stats.tweets(d, "rt_min", FUN = min, var = "retweet_count"),
    subject_stats.tweets(d, "rt_q25", FUN = quantile(probs = 0.25), var = "retweet_count"),
    subject_stats.tweets(d, "rt_q50", FUN = quantile(probs = 0.50), var = "retweet_count"),
    subject_stats.tweets(d, "rt_q75", FUN = quantile(probs = 0.75), var = "retweet_count"),
    subject_stats.tweets(d, "rt_max", FUN = max, var = "retweet_count"),
    subject_stats.tweets(d, "rt_IQR", FUN = IQR, var = "retweet_count"),
    subject_stats.tweets(d, "rt_M", FUN = mean, var = "retweet_count"),
    subject_stats.tweets(d, "rt_SD", FUN = sd, var = "retweet_count")
  )


# Fächer in Column
descr %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE) %>%
  column_spec(2, italic = TRUE, border_right = FALSE) %>%
  add_header_above(c(" " = 2, "Fächer" = 21))


# Fächer in Rows
descr %>%
  select(-N) %>% # remove rowsum of all states
  # Transpose Dataframe
  pivot_longer(-category) %>%
  pivot_wider(names_from = category, values_from = value) %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE)


# rm(descr, d)
```                                       
                                       
## Comparing classification methods
### Für Bundesländer
```{r}
summarise_matched_states.tweets <- function(data, category = "") {
  return(data %>%
    summarise(
      category = category,
      N = n(),
      BW = sum(matched_bw),
      BY = sum(matched_bayern),
      BE = sum(matched_berlin),
      BB = sum(matched_brandenburg),
      HB = sum(matched_bremen),
      HH = sum(matched_hamburg),
      HE = sum(matched_hessen),
      MV = sum(matched_mv),
      NI = sum(matched_nds),
      NW = sum(matched_nrw),
      RP = sum(matched_rlp),
      SL = sum(matched_saarland),
      SN = sum(matched_sachsen),
      ST = sum(matched_sachsenan),
      SH = sum(matched_sh),
      TH = sum(matched_thueringen)
    ))
}
```

#### Calculate tables
```{r}
descr <-
  rbind(
    # Hashtags only
    dat %>%
      summarise_states("Hashtags"),
    # TODO: change to .tweets
    # Tweets
    dat %>%
      summarise_matched_states.tweets("Simple Keywords")
  )



# Fächer in Column
descr %>%
  select(-N) %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE) %>%
  add_header_above(c(" " = 1, "Bundesländer" = 16))


# Fächer in Rows
descr %>%
  select(-N) %>% # remove rowsum of all states
  # Transpose Dataframe
  pivot_longer(-category) %>%
  pivot_wider(names_from = category, values_from = value) %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE)
```


### Für Fächer
```{r}
# matched with simple / main keywords
summarise_matched_subjects.tweets <- function(data, category = "") {
  return(data %>%
    summarise(
      category = category,
      N = n(), # sum is higher than total
      Biologie = sum(matched_biologie),
      Chemie = sum(matched_chemie),
      Deutsch = sum(matched_deutsch),
      Englisch = sum(matched_englisch),
      Erdkunde = sum(matched_erdkunde),
      Ethik = sum(matched_ethik),
      Franzoesisch = sum(matched_franzoesisch),
      Geschichte = sum(matched_geschichte),
      Informatik = sum(matched_informatik),
      Kunst = sum(matched_kunst),
      Mathe = sum(matched_mathe),
      Musik = sum(matched_musik),
      Paedagokik = sum(matched_paedagogik),
      Philosophie = sum(matched_philosophie),
      Physik = sum(matched_physik),
      Politik = sum(matched_politik),
      Psychologie = sum(matched_psychologie),
      Religion = sum(matched_religion),
      Spanisch = sum(matched_spanisch),
      Sport = sum(matched_sport),
      Wirtschaft = sum(matched_wirtschaft)
    ))
}
```

#### Calculate Tables
```{r}
descr <-
  rbind(
    # Hashtags only
    dat %>%
      summarise_subjects.tweets("Hashtags"),
    # Tweets
    dat %>%
      summarise_matched_subjects.tweets("Simple Keywords")
  )



# Fächer in Column
descr %>%
  select(-N) %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE) %>%
  add_header_above(c(" " = 1, "Fächer" = 21))


# Fächer in Rows
descr %>%
  select(-N) %>% # remove rowsum of all states
  # Transpose Dataframe
  pivot_longer(-category) %>%
  pivot_wider(names_from = category, values_from = value) %>%
  summary_kable() %>%
  column_spec(1, background = "lightgray", bold = TRUE)

# rm(descr)
```
