---
title: 'Subset Building'
output: html_document
---

```{r}
library(tidyverse)
library(kableExtra)
```

## Read in Complete Dataset
```{r}
dat <- readRDS("../DATA/TWITTER_DEUTSCHLAND_NOV_2020_FINAL.rds")
nrow(dat)
```

```{r}
results <- list()
```

## 1. User Keyword-based Method
```{r}
results <- dat %>% 
  filter(!is_retweet) %>% 
  filter(str_detect(description, regex("mathe|maths|physik|physics", ignore_case = TRUE))) 

results %>% select(text, description) %>% View()
```

```{r}
# Tweets not identified yet
rest <- anti_join(dat, results, by = "status_id")
```

### Mathematik
* #matheunterricht
* #mathematikunterricht
* #flippedmathe
* #mathelehrer
* #matheunterricht
* #letsrockmathe
* #mathelehrerinnen
* #matheabitur
* #mathelehrkräfte
* #mathematiklehrer
* #matheabi
* #mathematiklehrkräfte
* #mathenachhilfe
* #mathedidaktik
* #mathegym
* #mathematikdidaktik
* #mathematikförderwahn
* #matheabiturprüfung
* #mathebydanieljung
* #mathematikuntericht
* #mathelehren
* #mathematikdidaktikerinnen
* #mathematiklehrerin
* #mathelehrerin
* #pflichtfachmathe
* #pflichtfachmathematik
* #mathematiklehrerinnen
* #mathematiklehren
* #mathematiklehrkräften
* #mathetwitterlehrerzimmer
* #schulfachmathematik

### Physik

* #physikunterricht
* #leifiphysik
* #physiklehrer
* #physikdidaktik
* #physiklehrerinnen
* #pflichtfachphysik
* #physiklehrkräfte
* #physiknachhilfe
* #physiklehrerwettbewerb
* #didaktikphysik
* #physiklehrerzimmer
* #physikstunde
* #lieblingsfachphysik
* #mathephysikedchatde
* #physikedu
* #physiklk


## 2. Hashtag-based Method
```{r}
## Select all complete Hashtags

dat %>% select(hashtags) %>% pull()

dat$has_mathe


```


